---
title: "Who does more pushups"
author: Silvia Manzo
date: November 7, 2017
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

First i am going to do a variable analysis to analyze what information I need. I have two sets of data one is a numerical data called pushups and a catigorical data called positions. I plan to use a boxplot to display the data and use favstats as a numerical method to see if they are different. Finally I am going to use a ttest to make sense of this data. 




# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->
Based on the results found in graphical results boxplot, the median found for the line players was 14.5 and the median found for the skill players was 47.5. Also, on average the line players did more pushups than the skill players according to the boxplot, 24 by the skill player and 49 for the line players. 

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
myex <- gplot(push-ups,acs(x=position, y= pushups) myex + geom_boxplot myex + geom violin
```{r}
bwplot (pushups~position, data=pushups)
```

Based on the boxplot, the line players did about 24 pushups, as apposed to the skill players who did about 59 pushups. Therefore, we can say that the skill players did more puishups than the line players on average. 



## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
favstats (pushups~position, data=pushups)
```{r}
favstats (pushups~position, data=pushups)
```


# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
ttest (weight-position, data=pushups)
```{r}
t.test (pushups~position, data=pushups)
```


# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->
In conclusion, the results to the research question based on all data and analysis states that the line players do more pushups than the skill players on average. The line players did 59 pushups and the skill players did 24 pushups.
